% ========== USE CASE 8: Modular Loading - Full Features ==========
% This demonstrates full module loading for feature-rich documents
% All modules enabled for maximum functionality

\documentclass[11pt,a4paper]{article}
\usepackage{ifthen}

% ========== MODULE CONFIGURATION ==========
% FULL SETUP - All modules enabled
\newcommand{\EnableAdvancedTypography}{true}
\newcommand{\EnableMathematics}{true}
\newcommand{\EnableTables}{true}
\newcommand{\EnableBoxes}{true}
\newcommand{\EnableLists}{true}
\newcommand{\EnableCode}{true}
\newcommand{\EnableImages}{true}
\newcommand{\EnableAlgorithms}{true}
\newcommand{\EnableReferences}{true}

% ========== LOAD CONFIGURATION ==========
\input{config.tex}

% ========== DOCUMENT BEGIN ==========
\begin{document}

\title{Full Feature Configuration}
\author{LaTeX Expert}
\date{\today}
\maketitle

\begin{infobox}[title=Full Configuration]
This document showcases all available modules. Estimated compile time: 25-35 seconds. Best for  documents requiring all features.
\end{infobox}

\section{Advanced Typography}

\dropcap{W}{ith} advanced typography enabled, we can use sophisticated text formatting including drop caps, advanced font features, and enhanced spacing.

\section{Mathematical Excellence}

Complex mathematical expressions with full theorem environments:

\begin{theorem}[Fundamental Theorem of Calculus]
If $f$ is continuous on $[a,b]$ and $F$ is an antiderivative of $f$, then:
\begin{equation}
\int_a^b f(x) \, dx = F(b) - F(a)
\end{equation}
\end{theorem}

\begin{proof}
The proof follows from the definition of the definite integral and the properties of antiderivatives.
\end{proof}

\section{Algorithm Presentation}

\begin{algorithm}
\caption{Binary Search Algorithm}
\begin{algorithmic}[1]
\Procedure{BinarySearch}{$A, n, x$}
    \State $low \gets 1$
    \State $high \gets n$
    \While{$low \leq high$}
        \State $mid \gets \lfloor(low + high)/2\rfloor$
        \If{$A[mid] = x$}
            \State \textbf{return} $mid$
        \ElsIf{$A[mid] < x$}
            \State $low \gets mid + 1$
        \Else
            \State $high \gets mid - 1$
        \EndIf
    \EndWhile
    \State \textbf{return} $-1$
\EndProcedure
\end{algorithmic}
\end{algorithm}

\section{Code Highlighting}

\begin{lstlisting}[language=Python, caption=Python Example]
def fibonacci(n):
    """Calculate the nth Fibonacci number."""
    if n <= 1:
        return n
    else:
        return fibonacci(n-1) + fibonacci(n-2)

# Example usage
for i in range(10):
    print(f"F({i}) = {fibonacci(i)}")
\end{lstlisting}

\section{Enhanced Tables}

\begin{table}[htbp]
\caption{Feature Comparison Matrix}
\centering
\rowcolors{2}{rowalt}{white}
\begin{tabularx}{\textwidth}{L{3cm}C{2cm}C{2cm}C{2cm}X}
\rowcolor{headerbg}
\textcolor{headertext}{\textbf{Feature}} &
\textcolor{headertext}{\textbf{Basic}} &
\textcolor{headertext}{\textbf{Selective}} &
\textcolor{headertext}{\textbf{Full}} &
\textcolor{headertext}{\textbf{Description}} \\
\toprule
Typography & ✗ & ✗ & ✓ & Advanced font features \\
Mathematics & ✗ & ✓ & ✓ & Equations and theorems \\
Tables & ✗ & ✓ & ✓ & Professional data presentation \\
Boxes & ✓ & ✓ & ✓ & Information callouts \\
Lists & ✗ & ✓ & ✓ & Enhanced list formatting \\
Code & ✗ & ✗ & ✓ & Syntax highlighting \\
Images & ✗ & ✗ & ✓ & Advanced image handling \\
Algorithms & ✗ & ✗ & ✓ & Pseudocode presentation \\
References & ✗ & ✗ & ✓ & Bibliography management \\
\bottomrule
\end{tabularx}
\end{table}

\section{All Box Types}

\begin{successbox}
\textbf{Success:} Full configuration provides access to all available features and styling options.
\end{successbox}

\begin{warningbox}
\textbf{Warning:} Full feature loading increases compilation time but provides maximum flexibility.
\end{warningbox}

\begin{errorbox}
\textbf{Error Prevention:} Always test compilation time on your target platform before finalizing configuration.
\end{errorbox}

\section{Enhanced Lists}

\begin{enhancedlist}
    \item Full typography support with advanced spacing
    \item Mathematical expressions in list items: $\sum_{i=1}^n i = \frac{n(n+1)}{2}$
    \item Code snippets: \texttt{config.enableAll()}
    \item References to algorithms and figures
    \item Multi-level nested structures with consistent styling
\end{enhancedlist}

\section{References and Citations}

With the references module enabled, you can manage bibliographies and citations systematically for academic and professional documents.

\end{document}
